### 2020-03-16 writeup/setup.tex
wip

In the multi-task learning (MTL) problem, we are given the input of $k$ tasks $(X_1, Y_1), (X_2, Y_2), \dots, (X_k, Y_k)$.
We use a shared module $B$ for all tasks and a separate module $\set{A_i}_{i=1}^k$ for each task.
%    \paragraph{Different covariates:}
This corresponds to minimizing the following optimization objective.
\begin{align}
	\label{eq_mtl}
	f(B; A_1, \dots, A_k) = \sum_{i=1}^k \normFro{X_i B A_i - Y_i}^2.
\end{align}

@@

In this setting, we assume that the covariates of task $i$ are drawn from $\Sigma_i \in \real^{d \times d}$, but the models are the same across all the tasks, i.e.
\begin{align}
	y_i = X_i \beta + \varepsilon_i, \mbox{ with } \frac 1 {n_i} X_i^{\top}X_i \sim \Sigma_i
\end{align}

>>>>

In the multi-task learning (MTL) problem, we are given the input of $k$ tasks $(X_1, Y_1), (X_2, Y_2), \dots, (X_k, Y_k)$.
We use a shared body (module) $B$ for all tasks and a separate head (module) $\set{A_i}_{i=1}^k$ for each task.
%    \paragraph{Different covariates:}
This corresponds to minimizing the following optimization objective.
\begin{align}
	\label{eq_mtl}
	f(B; A_1, \dots, A_k) = \sum_{i=1}^k \normFro{X_i B A_i - Y_i}^2.
\end{align}
Note that we consider the natural parameterization without reweighting the tasks above.

@@

In this setting, we assume that the covariates of task $i$ are drawn from $\Sigma_i \in \real^{d \times d}$, but the models are the same across all the tasks, i.e.
\begin{align}
	Y_i = X_i \beta + \varepsilon_i. %, \mbox{ with } \frac 1 {n_i} X_i^{\top}X_i \sim \Sigma_i
\end{align}
